### 2015-05-26 Dissertation/abstract.tex
Updated abstract

We propose to extend this research to include the ``gray-box'' problem domain, which includes many
interesting real world problems. We plan to develop a variant of P3 which exploits
features of this domain, such as efficient local search and known variable linkage.
Furthermore, we want to examine how ``hamming ball search'' can be integrated into
global optimization, both through simple crossover and as part of P3.
Finally, we plan compare this P3 variant with state of the art black-box, gray-box, and
white box methods for solving challenging real world problems.
\end{doublespace}
\newpage

>>>>

P3 can be further improved by specializing to the gray-box domain, which includes
partial solution evaluation and known, limited, non-linear relationships between variables.
This Gray-Box P3 leverages the Hamming-Ball Hill Climber, an exceptionally efficient
form of local search, as well as a novel method for performing crossover using the
known variable interactions. In doing so Gray-Box P3 is able to find the global
optimum to very large problems in seconds, improving over Black-Box P3 by up to
two orders of magnitude.
\end{doublespace}
\newpage
